---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# iNZight Addons

Below is a list of available addons for iNZight.

```{r, echo = FALSE}
source('create_index.R')
tbl <- create_index()
MIN_VERSION <- ifelse(Sys.getenv("TRAVIS_BRANCH") == "master", 1, 0)
tbl <- tbl[tbl$Version >= numeric_version(MIN_VERSION), ]
tbl$Version <- as.character(tbl$Version)
if (nrow(tbl)) {
  write.dcf(tbl, "addons.txt")
  knitr::kable(tbl, row.names = FALSE)
} else {
  cat("", file = "addons.txt")
  cat("No addons are currently available.\n")
}
```

To install, download the file and install it from within iNZight:

- Open the __Advanced__ menu
- Choose __Manage modules__
- Click the __Browse__ button to locate the addon file
- Click __Install__

You can also __remove modules__ from __Manage modules__.


## Manual installation

To install addons manually, simply download the raw R file
and place it in your modules folder:

- Windows: `My Documents\iNZightVIT\modules`
- macOS: `Documents/iNZightVIT/modules`
- Linux: probably `~/Documents/iNZightVIT/modules`


## Making your own

To make your own, simply grab the `DemoModule.R` file and modify!
